---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package 
that provides functions for calculating probabilities of a Binomial random 
variable, and related calculations such as the probability distribution, 
the expected value, variance, mode, etc.


## Motivation

The creation of this package was used as a project assignment in one of the 
editions of [Stat 133 Concepts in Computing with Data](https://github.com/ucb-stat133).
The main purpose of this assignment was to illustrate some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
install.packages("devtools") 

# install "binomial"
devtools::install_github("gastonstat/binomial")
```


## Usage

```{r}
library(binomial)

# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)

# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
```


```{r}
 # binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```


```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

```{r}
 # binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```


### Binomial Random Variable

The package `"binomial"` also has the function `bin_variable()` that lets you 
create a binomial random variable. To be more precise, this function returns 
an object of class `"binvar"`

```{r}
# binomial variable
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1

# summary method
binsum1 <- summary(bin1)
binsum1
```


### Summary Meausres

Finally, `"binomial"` has a couple of additional functions to compute summary
measures such as the mean, variance, kurtosis

```{r}
# mean
bin_mean(10, 0.3)

# variance
bin_variance(10, 0.3)

# mode
bin_mode(10, 0.3)

# skewness
bin_skewness(10, 0.3)

# kurtosis
bin_kurtosis(10, 0.3)
```

