---
title: "Getting Started with binomial"
author: "Gaston Sanchez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## About `"binomial"`

The package `"binomial"` is a simple package to compute binomial probabilities, binomial distributions, as well as summary measures of a binomial random variable.


## Creating a binomial random variable

You can begin by creating a binomial random variable object with the function `bin_variable()`:

```{r}
binvar1 <- bin_variable(10, 0.3)
binvar1
```

The output of `bin_variable()` is an object of class `"binvar"`, which simply contains the parameters: number of trials, and probability of success.

Once you have a `"binvar"` object, you can get summary measures such as the mean, variance, mode, skewness and kurtosis, via the function `summary()`:

```{r}
summary(binvar1)
```


## Binomial Probability

To compute binomial probabilities, you should use the function `bin_probability`. This functions requires three inputs: number of successes, number of trials, and probability of success.

For example, say you want to compute the probability of 3 heads when tossing a fair coin 5 times:

```{r}
bin_probability(3, 5, 0.5)
```

If instead of a fair coin you suppose tossing a loaded coin with probability of heads 0.7, then:

```{r}
bin_probability(3, 5, 0.7)
```

You can also use `bin_probability()` to compute the probabilities for a range of successes. For example, the probabilities of less than 3 heads in 5 tosses of a fair coin is:

```{r}
bin_probability(0:3, 5, 0.5)
```


